{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-28 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

    Throughout, we define $F := f + g$ where $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex and $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. 
    We consider optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$ where the minimizer exists.

@@

>>>>

    Throughout, we make the following assumption unless specified. 
    \begin{assumption}[Smooth nonsmooth additive]\label{ass:smooth-nsmooth-additive}
        \;
            \item Define $F := f + g$. 
            \item $f: \RR^n \rightarrow \RR$ is $L$ Lipschitz smooth and $\mu \ge 0$ strongly convex. 
            \item $g: \RR^n \rightarrow \overline \RR$ is proper, closed and convex. 
            \item Minimizer exists for the optimization problem: $\min_x \left\lbrace f(x) + g(x)\right\rbrace$. 
    \end{assumption}

@@

        Let $F$ be given by Assumption \ref{ass:smooth-nsmooth-additive}. 
